Biden Projected to Win in the 2024 US Presidential Election

### 2024-03-15 paper/paper.qmd
sample of datasets to appendix added and intro modified

---
title: "Biden Projected to Win in the 2024 US Presidential Election"
author:
  - Monica Sainani
  - Kaavya Kalani
thanks: "Code and data supporting this analysis is available at: https://github.com/sainanim/Predictions-for-the-US-2024-Elections"
date: today
date-format: long
abstract: "This study investigates the dynamics of voting behaviour of americans leveraging demographic, socioeconomic, and geographic factors, such as age, family income, education, state of residency, and sex. We use a Bayesian Logistic Regression model with Post-Stratification to predict the outcome between Biden and Trump with the mentioned factors as predictors. Our study indictates that Biden is likely to be re-elected as the president with a 10% lead. This research contributes to a better understanding of the factors influencing political engagement in American democracy by offering insightful information that might guide future electoral strategies and policy discussion."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(rstan)
library(tidyverse)
library(arrow)
library(dplyr)
library(knitr)
library(ggplot2)
library(gutenbergr)
library(haven)
library(labelled)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(broom.mixed)
library(here)

poststrat_data <- arrow::read_parquet(file = here("data/analysis_data/poststrat_data.parquet"))
survey_data <- arrow::read_parquet(file = here("data/analysis_data/survey_data.parquet"))
us_election_model <- readRDS(file = here("models/single_bay.rds"))
```

@@

@@

library(modelsummary)
library(kableExtra)

@@

## Results
```{r}
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| warning: false
#| message: false

# Predictions and intervals from Bayesian model
library(rstan)

@@

@@

>>>>

---
title: "Biden Projected to Win in the 2024 US Presidential Election"
author:
  - Monica Sainani
  - Kaavya Kalani
thanks: "Code and data supporting this analysis is available at: https://github.com/sainanim/Predictions-for-the-US-2024-Elections"
date: today
date-format: long
abstract: "This study investigates the dynamics of voting behaviour of americans leveraging demographic, socioeconomic, and geographic factors, such as age, family income, education, state of residency, and sex. We use a Bayesian Logistic Regression model with Post-Stratification to predict the outcome between Biden and Trump with the mentioned factors as predictors. Our study indictates that Biden is likely to be re-elected as the president with a 10% lead. This research contributes to a better understanding of the factors influencing political engagement in American democracy by offering insightful information that might guide future electoral strategies and policy discussion."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

library(rstan)
library(tidyverse)
library(arrow)
library(dplyr)
library(knitr)
library(ggplot2)
library(gutenbergr)
library(haven)
library(labelled)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(broom.mixed)
library(here)
library(kableExtra)

# read the datasets and model
poststrat_data <- arrow::read_parquet(file = here("data/analysis_data/poststrat_data.parquet"))
survey_data <- arrow::read_parquet(file = here("data/analysis_data/survey_data.parquet"))
us_election_model <- readRDS(file = here("models/single_bay.rds"))
```

@@

The paper is further organised into three sections: Data, Model, Results, and Discussion. In the Data section, we discuss how the datasets to be used for the analysis were obtained and pre-processed. We will explain the variables of interest in the datasets for the analysis. The Model section describes the model being used for the analyis. The Results section will then highlight and discuss the trends and associations found during the analysis. Lastly, the Discussion section will talk about some interesting trends found in Results in depth, link it to the real world and also highlight the weaknesses of our analysis.

@@

@@

## Results
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-support-state
#| fig-cap: Estimated proportion support for Biden by State

@@

```
@fig-support-state

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-support-age
#| fig-cap: Estimated proportion support for Biden by Age Groups

@@

```
@fig-support-age

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-support-sex
#| fig-cap: Estimated proportion support for Biden by Sex

@@

```
@fig-support-sex

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-support-general
#| fig-cap: Estimated proportion support for Biden

@@

@fig-support-general

@@

# Appendix

## Cleaning

## Survey dataset
Here is a glimpse of the survey data set used

```{r}
head(survey_data)
```

## Poststratification dataset
Here is a glimpse of the poststratification data set used
```{r}
head(poststrat_data)
```

# References
